### 2014-04-20 Projects/DelCo_2014_04/Report/DelCo_2014.tex
DelCo: Add HOSE plots to report

@@

\chapter{Model Results}
\label{chap:Model_Results}

>>>>

% Center all figures
\makeatletter
\g@addto@macro\@floatboxreset\centering
\makeatother

@@

\chapter{Results}
\label{chap:Results}

\section{Hose Flow Tests}

\subsection{DNTADM}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTADM_BDP_A6}
\caption{BDP at interior door CD, Test DNTADM}
\label{fig:HOSE_DNTADM_BDP_A6}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTADM_BDP_A7}
\caption{BDP at exterior door A, Test DNTADM}
\label{fig:HOSE_DNTADM_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTADM_BDP_A8}
\caption{BDP at exterior door C\_West, Test DNTADM}
\label{fig:HOSE_DNTADM_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTADM_BDP_A9}
\caption{BDP at exterior door C\_East, Test DNTADM}
\label{fig:HOSE_DNTADM_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTADM_HOSE}
\caption{Hose pressure, Test DNTADM}
\label{fig:HOSE_DNTADM_HOSE}
\end{figure}

\clearpage

\subsection{DNTODF}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTODF_BDP_A6}
\caption{BDP at interior door CD, Test DNTODF}
\label{fig:HOSE_DNTODF_BDP_A6}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTODF_BDP_A7}
\caption{BDP at exterior door A, Test DNTODF}
\label{fig:HOSE_DNTODF_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTODF_BDP_A8}
\caption{BDP at exterior door C\_West, Test DNTODF}
\label{fig:HOSE_DNTODF_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTODF_BDP_A9}
\caption{BDP at exterior door C\_East, Test DNTODF}
\label{fig:HOSE_DNTODF_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTODF_HOSE}
\caption{Hose pressure, Test DNTODF}
\label{fig:HOSE_DNTODF_HOSE}
\end{figure}

\clearpage

\subsection{DSTADF}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTADF_BDP_A6}
\caption{BDP at interior door CD, Test DSTADF}
\label{fig:HOSE_DSTADF_BDP_A6}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTADF_BDP_A7}
\caption{BDP at exterior door A, Test DSTADF}
\label{fig:HOSE_DSTADF_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTADF_BDP_A8}
\caption{BDP at exterior door C\_West, Test DSTADF}
\label{fig:HOSE_DSTADF_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTADF_BDP_A9}
\caption{BDP at exterior door C\_East, Test DSTADF}
\label{fig:HOSE_DSTADF_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTADF_HOSE}
\caption{Hose pressure, Test DSTADF}
\label{fig:HOSE_DSTADF_HOSE}
\end{figure}

\clearpage

\subsection{DSTODF}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTODF_BDP_A6}
\caption{BDP at interior door CD, Test DSTODF}
\label{fig:HOSE_DSTODF_BDP_A6}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTODF_BDP_A7}
\caption{BDP at exterior door A, Test DSTODF}
\label{fig:HOSE_DSTODF_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTODF_BDP_A8}
\caption{BDP at exterior door C\_West, Test DSTODF}
\label{fig:HOSE_DSTODF_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTODF_BDP_A9}
\caption{BDP at exterior door C\_East, Test DSTODF}
\label{fig:HOSE_DSTODF_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTODF_HOSE}
\caption{Hose pressure, Test DSTODF}
\label{fig:HOSE_DSTODF_HOSE}
\end{figure}

\clearpage

\subsection{IMAODM}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMAODM_BDP_A6}
\caption{BDP at interior door CD, Test IMAODM}
\label{fig:HOSE_IMAODM_BDP_A6}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMAODM_BDP_A7}
\caption{BDP at exterior door A, Test IMAODM}
\label{fig:HOSE_IMAODM_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMAODM_BDP_A8}
\caption{BDP at exterior door C\_West, Test IMAODM}
\label{fig:HOSE_IMAODM_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMAODM_BDP_A9}
\caption{BDP at exterior door C\_East, Test IMAODM}
\label{fig:HOSE_IMAODM_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMAODM_HOSE}
\caption{Hose pressure, Test IMAODM}
\label{fig:HOSE_IMAODM_HOSE}
\end{figure}

\clearpage

\subsection{IMTADM}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMTADM_BDP_A6}
\caption{BDP at interior door CD, Test IMTADM}
\label{fig:HOSE_IMTADM_BDP_A6}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMTADM_BDP_A7}
\caption{BDP at exterior door A, Test IMTADM}
\label{fig:HOSE_IMTADM_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMTADM_BDP_A8}
\caption{BDP at exterior door C\_West, Test IMTADM}
\label{fig:HOSE_IMTADM_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMTADM_BDP_A9}
\caption{BDP at exterior door C\_East, Test IMTADM}
\label{fig:HOSE_IMTADM_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMTADM_HOSE}
\caption{Hose pressure, Test IMTADM}
\label{fig:HOSE_IMTADM_HOSE}
\end{figure}

\clearpage

\subsection{STODF Demonstration}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_STODF_demo_BDP_A6}
\caption{BDP at interior door CD, Test TODF\_Demo}
\label{fig:HOSE_STODF_demo_BDP_A6}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_STODF_demo_BDP_A7}
\caption{BDP at exterior door A, Test TODF\_Demo}
\label{fig:HOSE_STODF_demo_BDP_A7}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_STODF_demo_BDP_A8}
\caption{BDP at exterior door C\_West, Test TODF\_Demo}
\label{fig:HOSE_STODF_demo_BDP_A8}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_STODF_demo_BDP_A9}
\caption{BDP at exterior door C\_East, Test TODF\_Demo}
\label{fig:HOSE_STODF_demo_BDP_A9}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/HOSE/HOSE_STODF_demo_HOSE}
\caption{Hose pressure, Test TODF\_Demo}
\label{fig:HOSE_STODF_demo_HOSE}
\end{figure}
